---
title: "Introduction to MLRANOVA"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{introduction}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(MLRANOVA)
library(bench)
```
## Introduction
The '**MLRANOVA**' package provides functions for performing multivariate linear regression and analysis of variance (ANOVA). This vignette will guide you through using the main functionalities of the package.

## Multivariate Linear Regression
Multivariate linear regression is a statistical technique used to model the relationship between two or more predictor variables and a response variable by fitting a linear equation to the observed data.

### Example
The following example demonstrates how to perform multivariate linear regression with the '**multivariate_linear_regression**' function.

```{r}
# Simulate some data
set.seed(625)
X <- matrix(rnorm(500), ncol = 5)
Y <- X %*% c(1, 2, 3, 4, 5) + rnorm(100)

# Perform multivariate linear regression
model <- multivariate_linear_regression(X, Y)

# Display the coefficients of the model
print(model$coefficients)

# Comparison against the original R function 'lm' 
originallm <- lm(Y~X)
all.equal(as.numeric(originallm$coefficients), as.numeric(model$coefficients))
```

## ANOVA for Linear Regression Models
After fitting a linear regression model, it is common to perform ANOVA to understand the variation explained by the model compared to the total variation.

### Example
Using the model we fitted earlier, we can perform an ANOVA to test the overall significance of the model.

```{r, eval = FALSE}
# Perform ANOVA on the linear regression model
anova_result <- anova_linear_regression(model, X, Y)

# Display the ANOVA table
print(anova_result)

# Formatting to make comparison
original_anova <- as.data.frame(anova(originallm))
formatted_anova_result <- anova_result[1:2, c("Df", "Sum.Sq", "Mean.Sq", "F.value")]

# Rename columns to match
names(formatted_anova_result) <- names(original_anova)[1:4]

# Perform the comparison
comparison <- all.equal(original_anova[1:4], formatted_anova_result, tolerance = 1e-5, check.attributes = FALSE)

# Display the comparison result
print(comparison)
```

## Benchmarking

```{r}
# Benchmarking
benchmark_results <- bench::mark(
  "Original lm and ANOVA" = {
    originallm <- lm(Y~X)
    anova(originallm)
  },
  "MLRANOVA" = {
    model <- multivariate_linear_regression(X, Y)
    anova_linear_regression(model, X, Y)
  },
  iterations = 10,
  check = FALSE
)

# View the results
benchmark_results
```

## Summary
The '**MLRANOVA**' package simplifies the process of performing multivariate linear regression and subsequent ANOVA analysis. With just a few lines of code, you can fit models and evaluate their significance.

For more information on each function and additional options, please refer to the function documentation using the '?' operator in R (e.g., '**?multivariate_linear_regression**').


